---
title: "Using flashlight"
author: "Michael Mayer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{flashlight}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE,
  fig.width = 7,
  fig.height = 6
)
```

```{r setup}
library(flashlight)      # model interpretation
library(MetricsWeighted) # Metrics
library(dplyr)           # data prep
library(moderndive)      # data
library(caret)           # data split
library(xgboost)         # gradient boosting
library(ranger)          # random forest
```

## Introduction

In contrast to classic statistical modelling techniques like linear regression, modern machine learning approaches tend to provide black box results. In areas like visual computing or natural language processing, this is not an issue since there, focus usually lies on predicting things. Either the predictions are sufficiently useful in practice or the model won't be used. However, in areas where the purpose of a statistical model is also to explain or validate underlying theories (e.g. in medicine, economics, and biology), black box models are of little use. 

Thus, there is need to shed light into these black boxes resp. to explain machine learning models as good as possible. Of special interest are **model agnostic** approaches that work for any kind of modelling technique, e.g. a linear regression, a neural net or a tree-based method. The only requirement is the availability of a prediction function, i.e. a function takes a data set and returns predictions.

To do so is the purpose of the R package `flashlight`, which is inspired by the beautiful `DALEX` package, see (https://CRAN.R-project.org/package=DALEX). 

The main props of `flashlight`:

1. It is simple, yet flexible.

2. It offers model agnostic tools like model performance, variable importance, ICE profiles, partial dependence and further effects plots.

3. It allows to assess multiple models in parallel.

4. It supports "group by" operations.

5. It works with case weights.

Currently, models with numeric or binary response are supported.

We will now give a brief introduction to machine learning explanations and then illustrate them with the flashlight package.

## Background

Important model agnostic machine learning explanations include the following aspects, amongst many other.

### Model performance

How precise are models if applied to unseen data? This aspect is of key interest of basically any supervised machine learning model and helps to identify the best models or, if applied to subgroup, identify problematic segments with low performance. 

### Variable importance

Which variables are particularly relevant for the model? This aspect is helpful in different ways. Firstly, it might help to simplify the full modelling process by eliminating difficult to assess input variables with low explanatory power. Secondly, its pure information. Thirdly, it might help to identify problems in data structure: if one variable is extremely relevant and all others not, then there might be some sort of information leakage from the response. Thus said, variable importance considerations are very relevant for quality assurance as well. 

Different modelling techniques offer different ways of variable importance. In linear models, we consider e.g. F-test statistics or p values, in tree-based methods, its number of splits or avarage split gains etc. A model agnostic way to assess this is called *permutation importance*: For each input variable $X$, its values are randomly shuffled and the drop in performance with respect to a scoring function is calculated. The more important a variable, the larger the drop. If a variable can be shuffled without any impact on model precision, it is completely irrelevant. The method is described in Fisher et al. 2018 [1].

### Effects of input variables

In linear regression, the fitted model consists of an affine linear function in the inputs. Its coefficients immediately tell us how the response is expected to change if the value of one single input variable $X$ is systematically being adapted. How to describe such effects of a variable $X$ for more complex models that include non-linearities and high-order interactions?

One approach that is to study *Individual Conditional Expectation (ICE)* profiles of selected observations: They show how predictions of observation $i$ react when the input variable $X$ is systematically being changed, see [2]. The more different the profiles are in shape or slope, the stronger are the interaction effects. For a linear regression without interactions, all such profiles would be parallel.

If many ICE profiles are averaged, we get *partial dependence profiles* which can be viewed as the average effect of variable $X$, pooled over all interactions. Partial dependence plots where introduced in Friedman's seminal 2001 article on gradient boosting [3].

Studying ICE and partial dependence profiles make sense as long as it make sense to investigate the effect of $X$ while holding all other predictors fixed. An alternative to studying such *partial effects*, it is sometimes interesting to look at "accumulated" effects of $X$ including the effects from all other predictors. Such effects are estimated by averaging the predictions within values of the predictor $X$ of interest. If such prediction profile differs considerably from the observed average response, this might be a sign of model underfit. Residual profiles immediatly show such misfits as well. In classic statistical modelling, this sort of plots are called "fitted versus covariable" plots or "residual versus covariable" plots.

Besides looking at *average* profiles, it is often also revealing to consider *quartile* profiles or to visualized partial dependence, response and prediction profiles in the same plot.

The `flashlight` package offers these tools in a very simple way.

## Installation of `flashlight`

From CRAN:
```
install.packages("flashlight")
```

Latest version from github:
```
library(devtools)
install_github("mayer79/flashlight")
```

## Teaser

Let's start with an iris example.

```{r}
# Fit model
fit <- lm(Sepal.Length ~ ., data = iris)

# Make flashlight
fl <- flashlight(model = fit, data = iris, y = "Sepal.Length", label = "ols",
                 metrics = list(rmse = rmse, `R-squared` = r_squared))

# Performance: rmse and R-squared
plot(light_performance(fl), fill = "darkred")
plot(light_performance(fl, by = "Species"), fill = "darkred")

# Variable importance by drop in rmse
plot(light_importance(fl), fill = "darkred")
plot(light_importance(fl, by = "Species"), fill = "darkblue", alpha = 0.7)

# ICE profiles for Petal.Width
plot(light_ice(fl, v = "Petal.Width"), alpha = 0.4)
plot(light_ice(fl, v = "Petal.Width", by = "Species"))

# Partial dependence profiles for Petal.Width
plot(light_profile(fl, v = "Petal.Width"))
plot(light_profile(fl, v = "Petal.Width", by = "Species"))

# Observed, predicted, and partial dependence profiles
plot(light_effects(fl, v = "Petal.Width"))
plot(light_effects(fl, v = "Petal.Width", stats = "quartiles"))
eff <- light_effects(fl, v = "Petal.Width", by = "Species")
plot(eff) %>% 
  plot_counts(eff, alpha = 0.2)
```


## flashlights and multiflashlights

The process of using the `flashlight` package is as follows: 

1. Define a flashlight for each model. This is basically a list with optional components relevant for model interpretation:

   - `model`: The fitted model object like e.g. the one returned by `lm`.
   
   - `data`: A data set used to evaluate model agnostic tools, e.g. the validation data.
   
   - `y`: The name of the variable in `data` representing the model response.
   
   - `predict_function`: A function taking `model` and `data` and returning numeric predictions.
   
   - `linkinv`: Inverse link function used to retransform the values returned by `predict_function`. Defaults to the identity function `function(z) z`.
   
   - `w`: The name of the variable in `data` representing the case weights.
   
   - `by`: A character vector of names of grouping variables in `data`. These will be used to stratify all results.
   
   - `metrics`: A named list of metrics. These functions need to be available in the workspace and require arguments `actual`, `predicted`, `w` (case weights) as well as a placeholder ... for further arguments. All metrics available in R package `MetricsWeighted` are suitable.
   
   - `label`: The label of the model. This is the only required input when building the flashlight.
   
2. Calculate relevant information by calling the key functions:

   - `light_performance`: Calculates performance measures regarding different metrics, possibly within subgroups and weighted by case weights.
   
   - `light_importance`: Calculates variable importance (worsening in performance by random shuffling) for each or a subset of variables. Possibly within subgroups and using case weights. The most important variable names can be extracted by the function `most_important` on the result of `light_importance`.
   
   - `light_ice`: Calculates ICE profiles across a couple of observations, possibly within groups.
    
   - `light_profile`: Calculates partial dependent profiles across a covariable, possibly within groups. Generated by calling `light_ice` and aggregating the results. The function is flexible: it can also be used to generate response, residual or prediction profiles or calculate (weighted) quartiles instead of (weighted) means.
   
   - `light_effects`: Combines partial dependence, response and prediction profiles.
   
3. Plot the result: Each of these functions offer a `plot` method with minimal visualization of the results through `ggplot2`. The resulting plot can be customized by adding `theme` and other `ggplot` elements. If customization is insufficient, you can extract the data slot in the object returned by above key functions and build an own plot. 

In practice, multiple flashlights are being defined and evaluated in parallel. By the help of a `multiflashlight` object, The `flashlight` packages provides as much support as possible to avoid any redundancy. It can be used to combine fully specified flashlights or, and that is the more interesting option, take minimally defined flashlights (e.g. only `label`, `model` and `predict_function`) and add common arguments like `y`, `by`, `data` and/or `w` (case weights) in calling `multiflashlight`. If necessary, the resulting completed flashlights contained in the multiflashlight can be extracted again by `$`.

All key functions are defined for both `flashlight` and `multiflashlight` objects.

## Example

As illustration, we use the data set `house_prices` with information on `r nrow(house_prices)` houses sold in King County between May 2014 and May 2015. It is shipped along with R package `moderndive`.

The first few observations look as follows:

```{r}
head(house_prices)
```

Thus we have access to many relevant infos like size, condition as well as location of the objects. We want to use these variables to predict the (log) house prices by the help of the following regression techniques and shed some light on them: 

- linear regression,

- random forests, and

- boosted trees.

We use 70% of the data to calculate the models, 20% for evaluating their performance and for explaining them. 10% we keep untouched.

### Data preparation

Let's do some data preparation common for all models under consideration.

```{r}
prep <- transform(house_prices, 
                  log_price = log(price),
                  grade = as.integer(as.character(grade)),
                  year = factor(lubridate::year(date)),
                  age = lubridate::year(date) - yr_built,
                  zipcode = as.numeric(as.character(zipcode)),
                  waterfront = factor(waterfront, levels = c(FALSE, TRUE), labels = c("no", "yes")))

x <- c("grade", "year", "age", "sqft_living", "sqft_lot", "zipcode", 
       "condition", "waterfront")
```       

### Modelling

The random forest can directly work with this data structure. However, for the linear model, we need a small function with additional feature engineering, i.e. log transforming some input and categorizing the zipcode in large groups. Similarly, for XGBoost, such wrapper function turns non-numeric input variables to numeric. We will make use of these functions for both data preparation and prediction.
```{r}
# Data wrapper for the linear model
prep_lm <- function(data) {
  data %>% 
    mutate(sqrt_living = log(sqft_living),
           sqrt_lot = log(sqft_lot),
           zipcode = factor(zipcode %/% 10))
}

# Data wrapper for xgboost
prep_xgb <- function(data, x) {
  data %>% 
    select_at(x) %>% 
    mutate_if(Negate(is.numeric), as.integer) %>% 
    data.matrix()
}
```

Then, we split the data and train our models.

```{r}
# Train / valid / test split (70% / 20% / 10%)
set.seed(56745)
ind <- caret::createFolds(prep[["log_price"]], k = 10, list = FALSE)

train <- prep[ind >= 4, ]
valid <- prep[ind %in% 2:3, ]
test <- prep[ind == 1, ]

(form <- reformulate(x, "log_price"))
fit_lm <- lm(update.formula(form, . ~ . + I(sqft_living^2)), data = prep_lm(train))

# Random forest
fit_rf <- ranger(form, data = train, seed = 8373)
cat("R-squared OOB:", fit_rf$r.squared)

# Gradient boosting
dtrain <- xgb.DMatrix(prep_xgb(train, x), label = train[["log_price"]])
dvalid <- xgb.DMatrix(prep_xgb(valid, x), label = valid[["log_price"]])

params <- list(learning_rate = 0.5,
               max_depth = 6,
               alpha = 1,
               lambda = 1,
               colsample_bytree = 0.8)

fit_xgb <- xgb.train(params, 
                     data = dtrain,
                     watchlist = list(train = dtrain, valid = dvalid),
                     nrounds = 200, 
                     print_every_n = 100,
                     objective = "reg:linear",
                     seed = 2698)
```

### Creating the flashlights

Let's initialize a flashlight per model. Thanks to individual prediction functions, any model can be used in `flashlight`, even h2o and keras models.

```{r}
fl_mean <- flashlight(model = mean(train$log_price), label = "mean", 
                      predict_function = function(mod, X) rep(mod, nrow(X)))
fl_lm <- flashlight(model = fit_lm, label = "lm", 
                    predict_function = function(mod, X) predict(mod, prep_lm(X)))
fl_rf <- flashlight(model = fit_rf, label = "rf",
                    predict_function = function(mod, X) predict(mod, X)$predictions)
fl_xgb <- flashlight(model = fit_xgb, label = "xgb",
                     predict_function = function(mod, X) predict(mod, prep_xgb(X, x)))
print(fl_xgb)
```

What about all other relevant elements of a flashlight like the underlying data, the response name, metrics, retransformation functions etc? We could pass them to each of our flashlights. Or, we can combine the flashlights to a multiflashlight and pass additional common arguments there.

```{r}
fls <- multiflashlight(list(fl_mean, fl_lm, fl_rf, fl_xgb), y = "log_price", linkinv = exp, 
                       data = valid, metrics = list(rmse = rmse, `R-squared` = r_squared))
```

We could even extract these completed flashlights from the multiflashlight as if the latter is a list (actually it *is* a list with additional class `multiflashlight`).

```{r}
fl_lm <- fls$lm
```

### Assess performance

Let's compare the models regarding their validation performance.

```{r}
perf <- light_performance(fls)
perf
plot(perf)
```

Surprise, surprise: XGBoost is the winner! Now, black bars look a bit sad. Furthermore we would like to remove the x label.

```{r}
plot(perf, fill = "darkred") +
  xlab(element_blank())
```

The plot "politics" of `flashlight` is to provide simple graphics with minimal `ggplot`-tuning, so you are able to add your own modifications. If you are completely unhappy about the proposed plot (e.g. rather favour a scatterplot over a barplot), extract the `data` slot of `perf` and create the figure from scratch:

```{r}
head(perf$data)

perf$data %>% 
  ggplot(aes(x = label, y = value, group = metric, color = metric)) +
  geom_point() +
  scale_color_viridis_d(begin = 0.2, end = 0.6)
```

The same logic holds for all other main functions in the `flashlight` package.

For performance considerations, the minimum required info in the (multi-)flashlight are: "y", "predict_function", "model", "data" and "metrics". The latter two can also be passed on the fly.

### Variable importance

Now let's study variable importance of the explainers. By default, it is shown with respect to the first metric in the explainers. In our case, its the root-mean-squared error. 

```{r}
(imp <- light_importance(fls, n_max = 1000))
plot(imp)

```

Oops, what happened? Too many variables were tested for permutation drop in rmse, namely *all* in the data set, except the response. While this can be useful in certain situations, we will just pass the vector `x` of covariables. Furthermore we replace the metric to mean-squared error.

```{r}
(imp <- light_importance(fls, v = x, metric = list(mse = mse)))
plot(imp, fill = "darkred")
```

If we want to just extract the names of the most relevant three variables, we just do the following:

```{r}
most_important(imp, top_m = 3)
```

What about drop in R-squared? You don't have to update the multiflashlight with that new property. Instead, you can pass it to `light_importance` on the fly. `flashlight` does not know if higher or lower values in the scoring function are better, so you will need to pass that information manually.

```{r}
imp_r2 <- light_importance(fls, metric = list(r_squared = r_squared), 
                           v = x, lower_is_better = FALSE)
plot(imp_r2, fill = "darkred") +
  ggtitle("Drop in R-squared")
```
Minimal required elements in the (multi-)flashlight are the same as in `light_performance`.

Note: If the calculations take too long (e.g. large query data), set `n_max` to some reasonable value. `light_importance` will then randomly pick `n_max` rows and use only these for assessment of importance.

### Individual conditional expectation

How do predictions change when `sqft_living` changes alone? We can investigate this question by looking at "Individual Conditional Expectation" (ICE) profiles of a couple of observations.

```{r}
cp <- light_ice(fls, v = "sqft_living", n_max = 30, seed = 35)
plot(cp, alpha = 0.2)
```

The XGBoost profiles look wild - for real applications, setting monotonicity constraints would be an idea.

Note: Setting `seed` to a fixed value will ensure that the flashlights will consider the same rows. An alternative would be to pass a small subset of the data to `light_ice` and calculate all profiles or by passing row indices through `indices` for fixed selection.

### Partial dependence profiles

If many ICE profiles (in our case 1000) are averaged, we get an impression on the average effect of the considered variable. Such curves are called *partial dependence profiles* (PD) resp. *partial dependence plots*.

```{r}
pd <- light_profile(fls, v = "sqft_living")
pd
plot(pd)
```

The `light_profile` function offers different ways to specify the evaluation points of the profiles, e.g. by explicitly passing such points. 

```{r}
pd <- light_profile(fls, v = "sqft_living", pd_evaluate_at = seq(1000, 4000, by = 100))
plot(pd)
```

For discrete variables:

```{r}
pd <- light_profile(fls, v = "condition")
plot(pd)
```

In order to calculate ICEs and PDs, the following elements need to be available in the (multi-)flashlight: "predict_function", "model", "linkinv" and "data". "data" can also be passed on the fly.

### Profiles of predicted values, residuals, and response

We can use the function `light_profile` not only to create partial dependence profiles but also to get profiles of predicted values, responses or residuals. Additionally, we can either use averages or quartiles as summary statistics.

Average predicted values versus the living area are as follows:

```{r}
format_y <- function(x) format(x, big.mark = "'", scientific = FALSE)

pvp <- light_profile(fls, v = "sqft_living", type = "predicted", format = "fg", big.mark = "'")
plot(pvp) +
  scale_y_continuous(labels = format_y)
```

Note the formatting of y values as well as the `formatC` option `format = "fg"` and `big.mark` passed to the constructor of the x labels in order to improve basic appearance. We will recycle some of these settings for the next plots.

Similar the average response profiles (identical for all flashlights, to we only show one of them):

```{r}
rvp <- light_profile(fl_lm, v = "sqft_living", type = "response", format = "fg") 
plot(rvp) +
  scale_y_continuous(labels = format_y)
```

Same, but quartiles:

```{r}
rvp <- light_profile(fl_lm, v = "sqft_living", type = "response", 
                     stats = "quartiles", format = "fg") 
plot(rvp) +
  scale_y_continuous(labels = format_y)
```

What about residuals? First, we remove the "mean" flashlight by setting it NULL.

```{r}
fls$mean <- NULL
rvp <- light_profile(fls, v = "sqft_living", type = "residual", 
                     stats = "quartiles", format = "fg") 
plot(rvp) +
  scale_y_continuous(labels = format_y)
```

While the tree-based models have smaller residuals and medians close to 0, the linear model shows residual curvature that could be captured by representing `sqft_living` by more parameters.

If unhappy about the "group by" strategy, set `swap_dim` to TRUE.

```{r}
plot(rvp, swap_dim = TRUE) +
  scale_y_continuous(labels = format_y)
```

For less bars, set `n_bins` in `light_profile`:

```{r}
rvp <- light_profile(fls, v = "sqft_living", type = "residual", 
                     stats = "quartiles", format = "fg", n_bins = 5) 
plot(rvp, swap_dim = TRUE) +
  scale_y_continuous(labels = format_y)
```

For prediction profiles, the same elements as for ICE/PDs are required, while for response profiles we need "y", "linkinv" and "data". "data" can also be passed on the fly.

###  Visualizing different types of profiles as "effects" plot

In assessing the model quality, it is often useful to visualize

- response profile (quartiles or means),

- average predictions, and

- model effects (partial dependence profiles)

in the same plot and for each input variable. The `flashlight` package offers the function `light_effects` combine such profile plots:

```{r}
eff <- light_effects(fl_lm, v = "condition") 
p <- plot(eff) +
  scale_y_continuous(labels = format_y)
p
```

Let's add counts to see if the gaps between response and predicted profiles are problematic or just due to small samples.

```{r}
plot_counts(p, eff, alpha = 0.2)
```

The biggest gaps occur with very rare conditions, so the model looks quite fine. 

Note: Due to retransformation from log scale, the response profile is slightly higher than the profile of predicted values. If we would evaluate on the modelled log scale, that gap would vanish.

```{r}
eff <- light_effects(fl_lm, v = "condition", linkinv = I) 
p <- plot(eff) +
  scale_y_continuous(labels = format_y) +
  ggtitle("Effects plot on modelled log scale")
p
```

Besides adding counts to the figure, representing observed responses as boxplots (no whiskers and outliers in order to avoid too large y scale) might help to judge if there is a problematic misfit.

```{r}
eff <- light_effects(fl_lm, v = "condition", stats = "quartiles") 
p <- plot(eff, rotate_x = FALSE) +
   scale_y_continuous(labels = format_y)
plot_counts(p, eff, fill = "blue", alpha = 0.2, width = 0.3)
```

The `plot` method of `light_effects` allows to hide certain plot element if it looks too dense.

## Grouped calculations

A key feature of the `flashlight` package is to support grouped results. You can initialize the (multi-)flashlight with column names of one or many grouping variables or ask for grouped calculations in all major `flashlight` functions. Plots are adapted accordingly.

```{r}
fls <- multiflashlight(fls, by = "year")

# Performance
plot(light_performance(fls)) + 
  scale_fill_viridis_d(begin = 0.1, end = 0.9)

# With swapped dimension
plot(light_performance(fls), swap_dim = TRUE) + 
  scale_fill_viridis_d(begin = 0.1, end = 0.9)
  
# Importance
imp <- light_importance(fls, v = x)
plot(imp, top_m = 4)
plot(imp, swap_dim = TRUE)

# Effects: ICE
plot(light_ice(fls, v = "sqft_living", seed = 4345), 
     alpha = 0.8, facet_scales = "free_y") + 
  scale_color_viridis_d(begin = 0.1, end = 0.9) + 
  scale_y_continuous(labels = format_y)

# Effects: Partial dependence
plot(light_profile(fls, v = "sqft_living"))
plot(light_profile(fls, v = "sqft_living"), swap_dim = TRUE)

# Effects: Combined plot (only one flashlight) 
# -> we need to manually pass "by" or update the single flashlight
z <- light_effects(fls, v = "sqft_living", format = "fg", 
                   stats = "quartiles", n_bins = 5, by = NULL)
p <- plot(z) + 
  scale_y_continuous(labels = format_y) +
  coord_cartesian(ylim = c(0, 3e6))
plot_counts(p, z, alpha = 0.2)

```


## Working with case weights

In many applications, case weights are involved. All main functions in `flashlight` deal with them automatically. The only thing you need to do is to pass the column name of the column with case weights when initializing the (multi-)flashlight.

Let's go through the initial iris example again with (artificial) case weights:

```{r}
# Add weight info to the flashlight
fl_weighted <- flashlight(fl, w = "Petal.Length", label = "ols weighted")
fls <- multiflashlight(list(fl, fl_weighted))

# Performance: rmse and R-squared
plot(light_performance(fls))
plot(light_performance(fls, by = "Species"))

# Variable importance by drop in rmse
plot(light_importance(fls, by = "Species"))

# ICE profiles for Petal.Width 
# (not affected by weights because nothing is being aggregated)
indices <- seq(10, 150, by = 10)
plot(light_ice(fls, v = "Petal.Width", indices = indices), alpha = 0.2)
plot(light_ice(fls, v = "Petal.Width", by = "Species", indices = indices))

# Partial dependence profiles for Petal.Width
plot(light_profile(fls, v = "Petal.Width"))
plot(light_profile(fls, v = "Petal.Width", by = "Species"))

# Observed, predicted, and partial dependence profiles
plot(light_effects(fls, v = "Petal.Width"))
eff <- light_effects(fls, v = "Petal.Width", stats = "quartiles")
plot(eff) %>% 
  plot_counts(eff, alpha = 0.2, fill = "blue")
```

## Binary classification

The `flashlight` package works for numeric responses including binary targets.

```{r}
ir <- iris
ir$virginica <- ir$Species == "virginica"

fit <- glm(virginica ~ Sepal.Length + Petal.Width, data = ir, family = binomial)

# Make flashlight
fl <- flashlight(model = fit, data = ir, y = "virginica", label = "lr",
                 metrics = list(logLoss = logLoss, AUC = AUC), 
                 predict_function = function(m, d) predict(m, d, type = "response"))

# Performance: rmse and R-squared
plot(light_performance(fl), fill = "darkred")

# Variable importance by drop in rmse
plot(light_importance(fl), fill = "darkred")

# ICE profiles for Petal.Width
plot(light_ice(fl, v = "Petal.Width"), alpha = 0.4)

# Partial dependence profiles for Petal.Width
plot(light_profile(fl, v = "Petal.Width"))

# Observed, predicted, and partial dependence profiles
eff <- light_effects(fl, v = "Petal.Width")
plot_counts(plot(eff), eff, alpha = 0.2)
```

## References

[1] Fisher A., Rudin C., Dominici F. (2018). All Models are Wrong but many are Useful: Variable Importance for Black-Box, Proprietary, or Misspecified Prediction Models, using Model Class Reliance. ArXiv (arxiv.org/abs/1801.01489).

[2] Goldstein, A. et al. Peeking inside the black box: Visualizing statistical learning with plots of individual conditional expectation. Journal of Computational and Graphical Statistics, 24:1, 2015 (https://doi.org/10.1080/10618600.2014.907095).

[3] Friedman J. H. Greedy function approximation: A gradient boosting machine. The Annals of Statistics, 29:1189–1232, 2001 (https://doi.org/10.1214/aos/1013203451).

